### 2021-06-03 sections/introduction.tex
update introduction

Following the observation of the Higgs boson by the ATLAS and CMS experiments~\cite{Aad:2012tfa,Chatrchyan:2012ufa} at
the Large Hadron Collider (LHC), a comprehensive programme of measurements of its properties is underway.
%looking for deviations from the Standard Model (SM) predictions.  
An interesting possibility is the presence of flavour-changing neutral-current (FCNC) interactions 
between the Higgs boson, the top quark, and a $u$- or $c$-quark, $tqH$ ($q=u,c$). Since the Higgs boson is lighter than the top quark~\cite{Aad:2015zhl}, 
%with a measured mass $m_H=125.09 \pm 0.24~\gev$~\cite{Aad:2015zhl}, 
such interactions would manifest themselves as FCNC top-quark decays~\cite{Agashe:2013hma}, $t\to H q$.  
In the Standard Model (SM), such decays are suppressed relative to the dominant $t\to Wb$ decay mode, since $tqH$ 
interactions are forbidden at the tree level and suppressed even at higher orders in the perturbative expansion due to the 
Glashow--Iliopoulos--Maiani (GIM) mechanism~\cite{Glashow:1970gm}.  As a result, the SM predictions for the $t \to Hq$ branching 
ratios ($\BR$) are exceedingly small, $\BR(t\to Hu) \sim 10^{-17} $ and $\BR(t\to Hc) \sim 10^{-15}$~\cite{Eilam:1990zc,Mele:1998ag,AguilarSaavedra:2004wm,Zhang:2013xya}, making them undetectable in the foreseeable future.
In contrast, large enhancements of these branching ratios are possible in some scenario beyond the SM.
Examples include quark-singlet models~\cite{AguilarSaavedra:2002kr}, two-Higgs-doublet models (2HDM) of type I, with explicit flavour conservation,
and of type II, such as the minimal supersymmetric SM (MSSM)~\cite{Bejar:2000ub, Guasch:1999jp,Cao:2007dk,Cao:2014udj}, supersymmetric models
with R-parity violation~\cite{Eilam:2001dh}, composite Higgs models with partial compositeness~\cite{Azatov:2014lha}, 
or warped extra dimensions models with SM fermions in the bulk~\cite{Azatov:2009na}. 
In these scenarios, branching ratios can be as high as $\BR(t\to Hq) \sim 10^{-5}$. 
An even larger branching ratio of  $\BR(t\to Hc) \sim 10^{-3}$ can be reached in 2HDM without explicit flavour conservation (type III),
since a tree-level FCNC coupling is not forbidden by any symmetry~\cite{Cheng:1987rs,Baum:2008qm,Chen:2013qta,Chiang:2015cba,Crivellin:2015hha,Botella:2015hoa, Gori:2017tvg,Chiang:2017fjr}. 
While other FCNC top couplings ($tq\gamma$, $tqZ$, $tqg$) are also enhanced in these scenarios beyond the SM, 
the largest enhancements are typically found for the $tqH$ couplings, and in particular the $tcH$ coupling~\cite{Agashe:2013hma}.

@@

of top-quark pair ($\ttbar$) events collected in proton-proton ($pp$) collisions at centre-of-mass energies of $\sqrt{s}=7~\tev$ and $8~\tev$~\cite{Aad:2014dya,Aad:2015pja,Khachatryan:2016atv} during Run~1 of the LHC, as well as at $\sqrt{s}=13~\tev$~\cite{Aaboud:2017mfd,Aaboud:2018pob,Sirunyan:2017uae} using early Run~2 data.

@@

of $\BR(H\to b\bar{b})\simeq 58\%$. Compared with Run~1, the Run~2 searches benefit from the increased $\ttbar$ cross section at $\sqrt{s}=13~\tev$, 
as well as the larger integrated luminosity.

@@

@@

%The searches presented in this paper are focused on the dominant fermionic decay modes of the Higgs boson.
The searches presented in this paper are focussed on fermionic decay modes of the Higgs boson. Therefore, they help to complete the 
ATLAS experiment's programme of searches for $t \to Hq$ decays based on $pp$ collision
%programme of searches for $t \to Hq$ decays of the ATLAS experiment based on $pp$ collision 
data at $\sqrt{s}=13~\tev$ recorded in 2015 and 2016. The corresponding integrated luminosity is 36.1 fb$^{-1}$.
Two analyses are performed, searching for $\ttbar \to WbHq$ production (ignoring $pp \to tH$ production) and targeting the 
$H \to b\bar{b}$ and $H \to \tau^+\tau^-$ decay modes, which this paper refers to as ``$\Hbb$ search'' and ``$\Htautau$ search'', respectively.
The $\Hbb$ search selects events with one isolated electron or muon from the $W \to \ell\nu$ decay, and multiple jets, several 
of which are identified with high purity as originating from the hadronisation of $b$-quarks. 
%The $\Htautau$ search selects events with either one or two hadronically decaying $\tau$-lepton candidates, as well as multiple jets. 
The $\Htautau$ search selects events with two $\tau$-lepton candidates, at least one of which decays hadronically, as well as multiple jets.
The latter requirement aims to select events with a hadronically decaying $W$ boson, since this allows an improved reconstruction of the
event kinematics.

%two of which originating from hadronic $W$ decays. 
Both searches employ multivariate techniques to discriminate between the signal and the background on the basis of their different kinematics. 
These two searches are combined with previous ATLAS searches in the diphoton and multilepton final states using the same dataset~\cite{Aaboud:2017mfd,Aaboud:2018pob}, and bounds are set on $\BR(t\to Hc)$ and $\BR(t\to Hu)$, as well as on the corresponding non-flavour-diagonal Yukawa couplings. 
The combination is performed after verifying the overall consistency of the results obtained by the different searches, which exploit very different
experimental signatures and thus are affected by different backgrounds and related systematic uncertainties. 
By combining all searches, the expected sensitivity is improved by about a factor of two relative to the most sensitive individual results.

>>>>

It has been nearly a decade since the observation of Higgs boson by the ATLAS and CMS experiments~\cite{Aad:2012tfa,Chatrchyan:2012ufa} at
the Large Hadron Collider (LHC), a comprehensive programme of measurements of its properties was conducted, by which no significant sign of deviation from Standard Model (SM) was observed until today. But there is still chance finding new physics with searches already attempted but with higher sensitivity. An interesting possibility is the presence of flavour-changing neutral-current (FCNC) interactions 
between the Higgs boson, the top quark, and a $u$- or $c$-quark, $tqH$ ($q=u,c$). Since the Higgs boson is lighter than the top quark~\cite{Aad:2015zhl}, 
%with a measured mass $m_H=125.09 \pm 0.24~\gev$~\cite{Aad:2015zhl}, 
such interactions would manifest themselves as FCNC top-quark decays~\cite{Agashe:2013hma}, $t\to H q$.  
In the Standard Model (SM), such decays are suppressed relative to the dominant $t\to Wb$ decay mode, since $tqH$ 
interactions are forbidden at the tree level and suppressed even at higher orders in the perturbative expansion due to the 
Glashow--Iliopoulos--Maiani (GIM) mechanism~\cite{Glashow:1970gm}.  As a result, the SM predictions for the $t \to Hq$ branching 
ratios ($\BR$) are exceedingly small, $\BR(t\to Hu) \sim 10^{-17} $ and $\BR(t\to Hc) \sim 10^{-15}$~\cite{Eilam:1990zc,Mele:1998ag,AguilarSaavedra:2004wm,Zhang:2013xya}, making them undetectable in the foreseeable future.
In contrast, large enhancements of these branching ratios are possible in some scenarios beyond the SM.
Examples include quark-singlet models~\cite{AguilarSaavedra:2002kr}, two-Higgs-doublet models (2HDM) of type I, with explicit flavour conservation,
and of type II, such as the minimal supersymmetric SM (MSSM)~\cite{Bejar:2000ub, Guasch:1999jp,Cao:2007dk,Cao:2014udj}, supersymmetric models
with R-parity violation~\cite{Eilam:2001dh}, composite Higgs models with partial compositeness~\cite{Azatov:2014lha}, 
or warped extra dimensions models with SM fermions in the bulk~\cite{Azatov:2009na}. 
In these scenarios, branching ratios can be as high as $\BR(t\to Hq) \sim 10^{-5}$. 
An even larger branching ratio of  $\BR(t\to Hc) \sim 10^{-3}$ can be reached in 2HDM without explicit flavour conservation (type III),
since a tree-level FCNC coupling is not forbidden by any symmetry~\cite{Cheng:1987rs,Baum:2008qm,Chen:2013qta,Chiang:2015cba,Crivellin:2015hha,Botella:2015hoa, Gori:2017tvg,Chiang:2017fjr}. 
While other FCNC top couplings ($tq\gamma$, $tqZ$, $tqg$) are also enhanced in these scenarios beyond the SM, 
the largest enhancements are typically found for the $tqH$ couplings, and in particular the $tcH$ coupling~\cite{Agashe:2013hma}.

@@

of top-quark pair ($\ttbar$) events collected in proton-proton ($pp$) collisions at centre-of-mass energies of $\sqrt{s}=7~\tev$ and $8~\tev$~\cite{Aad:2014dya,Aad:2015pja,Khachatryan:2016atv} during Run~1 of the LHC, as well as at $\sqrt{s}=13~\tev$~\cite{fcnc36} using early Run~2 data.

@@

of $\BR(H\to b\bar{b})\simeq 58\%$. Compared with Run~1, the Run~2 searches benefit from the increased $\ttbar$ cross section at $\sqrt{s}=13~\tev$, as well as the larger integrated luminosity.

@@

The searches with  $H\to \tau^+\tau^-$ and $H\to b\bar{b}$ decays are later published~\cite{fcnc36}, unfortunately with no FCNC signal found. Combining all of the ATLAS searches using 36fb$^{-1}$ Run~2 data, the limits at 95\% CL are set for  $\BR(t\to Hc)<0.11\%$ and $\BR(t\to Hc)<0.12\%$ respectively assuming the other one is 0.

@@

%The searches presented in this paper are focused on the dominant fermionic decay modes of the Higgs boson.
This paper is focussed on the tau decay mode of the Higgs boson with the complete dataset collected during the Run~2 from 2016 to 2018. The corresponding integrated luminosity is 139.6 fb$^{-1}$. Both $\ttbar \to WbHq$ decay and $pp \to tH$ production are targeted. Events with two hadronically decaying $\tau$-lepton candidate (\tauhad) are selected for hadronic channels. Events with at least one \tauhad with an additional electron or muon are selected from leptonic channels, which exploits more regions compared to the search conducted using partial Run~2 data.

Multivariate technique is used to discriminate between the signal and the background on the basis of their different kinematics.

The expected sensitivity is about a factor of two relative to the most sensitive results~\cite{fcnc36} up until now.
